Homework 4

### 2013-02-19 hw4/document/hw4.tex
filled in the remaining homework questions

@@

@@

@@

Since it was an abstract piece of art, we did not have particular expectations. Wer

@@

@@

>>>>

We choose an abstract painting from Picasso because we were interested in seeing what concepts different people see in a work of art in which the main message is suggested, hinted upon, rather than revealed upfront.

@@

We got a java word cloud from GitHub (epicdevs/Word-Cloud). It takes a list of strings as input and outputs a BufferedImage which we flushed to file as a PNG.

@@

We got an interesting blend of concepts. Initially we assumed that \emph{music}, \emph{sentiment} or \emph{melange} would be among of the top hits.

@@

Since it was an abstract piece of art, we did not have particular expectations. They could have either converged to a core of concepts, or could have yielded unique results.

@@

Insted of using only one image, we could use a batch of different images built around the same concept.

@@

By getting first impressions, we align ourselves with the global perception. When working in the studio, it is easy to get a skewed perception, to derail from the global train of thought. By getting valuable feedback from the outsied, we align ourselves once more with reality.
